Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2016-05-12 paper/paper.tex
Mass reorganization

\cite{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) \vnote{With what?}.  Although the correlation in the plasma trough was not calculated, the data presented \vnote{for X events} show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).

>>>>

\cite{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) \inote{With what?}.  Although the correlation in the plasma trough was not calculated, the data presented \inote{for X events} show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
